Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex

 \item The Bayesian framework of \cite{viappiani2010optimal} using Monte Carlo methods for Bayesian inference and asking choice queries (asking the user to select its preferred item among a set of displayed ones); the next query is computed by performing a greedy optimization of {\em Expected Utility of a Selection} (hereafter just called {\sc EUS}), a submodular quantity that can be used as a proxy for value of information (giving strong approximate guarantees).

@@

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. According to the classical
(without indifference) Bradley-Terry model~\cite{BraTer52}, when queried about a pair
of configurations, the probability that a user will prefer
configuration $\vx^i$ over the alternative $\vx^j$ amounts to:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
In other words, the probability grows with the difference between the
utilities of the two items. Support for indifference has been
introduced in~\cite{guo2010real} by postulating that the probability
of the user being indifferent about the two configurations depends on
how close their utilities are, as in the exponential distribution:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations, as in~\cite{guo2010real}.

% \footnote{When experiment with EUS and QI, the user is forced to select
% its preffered item, so indifference is not possible. While support for indifference
% could be added, we chose to .}
%\andrea{@paolo: e' necessaria la footnote? dobbiamo tagliare..}

>>>>

 \item The Bayesian framework of \cite{viappiani2010optimal} using Monte Carlo methods
 \footnote{We use 50000 particles to represent the probability distribution.}for Bayesian inference and asking choice queries (asking the user to select its preferred item among a set of diplayed ones); the next query is computed by performing a greedy optimization of {\em Expected Utility of a Selection} (hereafter just called {\sc EUS}), a submodular quantity that can be used as a proxy for value of information (giving strong approximate guarantees).

@@

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. According to the classical
(without indifference) Bradley-Terry model~\cite{BraTer52}, when queried about a pair
of configurations, the probability that a user will prefer
configuration $\vx^i$ over the alternative $\vx^j$ amounts to:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
In other words, the probability grows with the difference between the
utilities of the two items. Support for indifference has been
introduced in~\cite{guo2010real} by postulating that the probability
of the user being indifferent about the two configurations depends on
how close their utilities are, as in the exponential distribution:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations\footnote{When experimenting with EUS and QI, the user is
  forced to select its preffered item, so indifference is not
  possible. While support for indifference could be added, we chose to
  be consistent with the methods as originally published.}, as
in~\cite{guo2010real}.
%\andrea{@paolo: e' necessaria la footnote? dobbiamo tagliare..}
